A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by organization x.}

### 2021-09-02 paper.tex
Figures Update
New figures added to paper.

\begin{document}
%
\title{A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by organization x.}}
% (Biological) Life-Cycle Algorithm: A novel distributed nature-inspired algorithm for solving optimization problems
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 150--250 words.

@@

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}

@@

One of the publications with the most influence on our research proposes a
cloud-native optimization framework, that can include multiple
(population-based) algorithms [1]. In their research, they work with ideas such
as:

These ideas planted the seed of thought in our current presentation.

@@

In this paper, we present an algorithm inspired by the biological life-cycle of
animal species, which consists of several stages: birth, growth, reproduction,
and death. As in nature, we intend to execute all these stages in parallel and
asynchronously on a population that evolves constantly.

@@

@@

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

>>>>

\begin{document}
%
\title{A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by organization x.}}
% (Biological) Life-Cycle Algorithm: A novel distributed nature-inspired algorithm for solving optimization problems
%
\titlerunning{Life-Cycle Algorithm}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{J. C. Felix-Saul \inst{1} \and
Mario García Valdez\inst{1} \and
Juan J. Merelo Guervós\inst{2}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Department of Graduate Studies, Tijuana Institute of Technology, Tijuana, Mexico \and
Department of Computer Architecture and Technology, Universidad de Granada, Granada, Spain}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 150--250 words.

@@

\keywords{Distributed Bioinspired Algorithms  \and Genetic Algorithms \and Cloud Computing.}
\end{abstract}

@@

One of the publications with the most influence on our research proposes a
cloud-native optimization framework, that can include multiple
(population-based) algorithms [1]. In their research, they work with ideas such
as those mentioned in Fig.~\ref{fig1}.

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig1_background.pdf}
    \caption{These ideas planted the seed of thought in our current presentation.} \label{fig1}
    \end{figure}

@@

In this paper, we present an algorithm inspired by the biological life-cycle of
animal species, which consists of several stages: birth, growth, reproduction,
and death. As in nature, we intend to execute all these stages in parallel and
asynchronously on a population that evolves constantly. We show the LifeCycle 
Algorithm Proposal Model in Fig.~\ref{fig2}.

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig2_proposal.pdf}
    \caption{LifeCycle Algorithm Proposal Model.} \label{fig2}
    \end{figure}

@@

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig9}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig9}
\end{figure}
